%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.3in,right=0.4in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Linke (Linda) Wang} % Your name
\address{Looking for Software Development Internship \\ https://www.linkedin.com/in/linke-wang-a7472814/} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(216) 235-6368 \\ 117 Hayes Ave, San Jose, CA95123 \\ linkw75@gmail.com \\ https://github.com/linkw1992} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Northeastern University, San Jose, CA} \hfill {\em Sep. 2018 - Present} 
\\ Master of Science in Information Systems, Major in Computer Software Engineering \\ 
{\bf University of Connecticut, Storrs, CT} \hfill {\em Sep. 2009 - May 2011} 
\\ Master of Science in Statistics\\ 
{\bf Nankai University, Tianjin, China} \hfill {\em Sep. 2005 - Jun. 2009} 
\\ Bachelor of Science in Mathematics and Applied Mathematics.\\
**Received Scholarship\\ 
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages &  Java, Python, C++, HTML, CSS, JavaScript, MATLAB, SAS\\
Frameworks & React(ES6), Bootstrap, AngularJS, NodeJS, JQuery, Spring, SpringMVC, Mybatis\\
Tools & Eclipse, Sublime, JetBrains WebStorm, mySQL, MongoDB, Tomcat, Maven\\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Relevant Experience}

\begin{rSubsection}{Sinosoft Company Limited, Beijing, China}{Jun. 2018 - Aug. 2018}{}{}
\item Built webpages via html, css, and JS frameworks like AngularJS and JQuery.  
\item Learnt the application of Modules and Components on real software development. Learnt to comprehend product requirement documents, to test and design test case, to do code review, and to cooperate with other team members.
\end{rSubsection}

\end{rSection}



%----------------------------------------------------------------------------------------
%	Projects SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{SOFTWARE DEVELOPMENT PROJECTS}
\begin{rSubsection}{Users Information Management (Maven, Spring, SpringMVC, Mybatis, MySql)}{Aug 2018 - Sep 2018}{}{}
\item Made interfaces and implements, configurations and tests. Created distributed database.
\item Divided the project into submodules according to document requirement, in order to manage development and deployment. 
\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{Early-Bird Webpage (HTML, CSS, JavaScript, React(es6), GraphQL, Bootstrap, Sublime, Django, NodeJS, etc)}{June 2018 - July 2018}{}{}
\item Aimed to make a table to display all users' data, and realized the function that sorting and selecting by users' name, score each week, or cumulative score.
\item Separated the components and wrote the function algorithm, configurated them with existing data, then combined them and completed the table via css.
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Mock Steam Platform (HTML, CSS, JavaScript, Java, jsp, Eclipse, mySQL, Tomcat)}{May 2018 - June 2018}{}{}
\item Realized registration, login as user/administrator, logout functions.
\item Debugged the JS part via breakpoint and console.log. Completed the algorithm, then we could choose to register and login as common user or administrator.
and run the code to configurate 
\end{rSubsection}

\end{rSection}






%----------------------------------------------------------------------------------------
\begin{rSection}{Relevant Courses} \itemsep -3pt
\item Data Structure and Algorithms, Computer Operating System and Network, Mathematical Software, Statistical Computing and Statistical Packages, Mathematical Modeling, Application Engineering and Development, Data Management and Database Design 
% \\ \itab{Process Control (ongoing)} \tab{} \tab{Electrodynamics}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Professional Presentations}{}{} \itemsep -3pt
\begin{rSubsection}{}{}{}{}
\item Presentation \textit{Agricultural productivity growth in New England: Will climate change matter?} in Joint AAEA \& NAREA Conference, Pittsburgh, PA, July 2011.
The second author, with first author Deep Mukherjee. The main purpose of this presentation is to analyze the relationship between agricultural productivity and factors relevant to weather. This presentation have at least 100 people joint in. 
\item National Olympiad in Informatics in Provinces Semi-Final Candidate in 2001 (QBASIC Group)
\end{rSubsection}
\end{rSection}

\end{document}
